%----------------------------------------------------------------------------------------
%  SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%  SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

  %------------------------------------------------

  \cventry
  {Associate Consultant (Java Backend Developer)} % Job title
  {Link Consulting} % Organization
  {Lisbon, Portugal (Remote)} % Location
  {Feb. 2023 - Present} % Date(s)
  { % Description(s) of tasks/responsibilities
    \begin{cvitems}
      \item {\textbf{EMSA - Maritime Safety (Dec. 2025 - Present)}
        \begin{itemize}[leftmargin=1.5em, itemsep=0.2em]
          \item {Integrated into a smaller team with the task of taming the jungle of old WebLogic services that support EMSA's safety and monitoring systems for European waters.}
          \item {Focused on refactoring and migrating legacy services to modern Spring Boot applications, improving maintainability and performance.}
        \end{itemize}}
      \item {\textbf{MaxMat - Retail (Nov. 2024 - Dec. 2025)}
        \begin{itemize}[leftmargin=1.5em, itemsep=0.2em]
          \item {Worked on the Azure architecture for MaxMat's warehouse management and international e-commerce integrations.}
          \item {Initially focused on designing backend solutions to streamline operations and enable seamless integration with external systems.}
          \item {Later led the Dev core team, while focusing on the DevOps side of the project, implementing CI/CD pipelines and infrastructure as code using Bicep and Azure native services.}
        \end{itemize}}
      \item {\textbf{HF GIRO - Public Transport (Feb. 2023 - Nov. 2024)}
        \begin{itemize}[leftmargin=1.5em, itemsep=0.2em]
          \item {Worked on the HF GIRO system, the public transport solution for Madeira, enabling better management of ticketing and transportation networks.}
          \item {Developed backend services with Java and Spring Boot, ensuring seamless integration with payment systems and real-time data processing.}
          \item {Addressed technical challenges, including ensuring high availability and scaling the system for increased usage during peak times.}
        \end{itemize}}
    \end{cvitems}
  }

  \vspace{0.4cm}

  %------------------------------------------------

  \cventry
  {Junior Consultant (Java Backend Developer)} % Job title
  {Link Consulting} % Organization
  {Lisbon, Portugal} % Location
  {Jul. 2022 - Feb. 2023} % Date(s)
  { % Description(s) of tasks/responsibilities
    \begin{cvitems}
      \item {\textbf{Transportes Metropolitanos de Lisboa (TML)}
        \begin{itemize}[leftmargin=1.5em, itemsep=0.2em]
          \item {Contributed to developing the Transportes Metropolitanos de Lisboa system, managing public transportation across the Lisbon metropolitan area.}
          \item {Focused primarily on backend development with Java and Spring Boot, while also handling challenges in frontend and DevOps.}
          \item {Worked on payment gateway integration, ticketing systems, and data management systems to support operational needs.}
        \end{itemize}}
    \end{cvitems}
  }

  \vspace{0.4cm}

  %------------------------------------------------

  \cventry
  {Backend Intern} % Job title
  {Optiply} % Organization
  {Évora, Portugal} % Location
  {Mar. 2022 - Jun. 2022} % Date(s)
  { % Description(s) of tasks/responsibilities
    \begin{cvitems}
      \item {\textbf{Backend Internship}
        \begin{itemize}[leftmargin=1.5em, itemsep=0.2em]
          \item {Completed a three-month internship in backend development. The internship consisted of a formative phase with Udemy courses and a project phase.}
          \item {Developed a reactive microservice in Micronaut to manage webshop specifications and settings, storing data in a PostgreSQL database and using Project Reactor, gRPC, and Protobuf.}
        \end{itemize}}
    \end{cvitems}
  }

  \vspace{0.4cm}

  %------------------------------------------------

  \cventry
  {Cybersecurity Intern} % Job title
  {NOVABASE} % Organization
  {Lisbon, Portugal} % Location
  {Nov. 2016 - Feb. 2017} % Date(s)
  { % Description(s) of tasks/responsibilities
    \begin{cvitems}
      \item {\textbf{Wireless Intrusion Detection System (wIDS)}
        \begin{itemize}[leftmargin=1.5em, itemsep=0.2em]
          \item {Participated in a professional internship focused on a wireless intrusion detection system (wIDS), which expanded my knowledge in penetration testing, networks, Linux, and coding.}
        \end{itemize}}
    \end{cvitems}
  }

  \vspace{0.4cm}

  %------------------------------------------------

  \cventry
  {Tech Support Intern} % Job title
  {Vodafone Portugal} % Organization
  {Lisbon, Portugal} % Location
  {May 2016 - Jun. 2016} % Date(s)
  { % Description(s) of tasks/responsibilities
    \begin{cvitems}
      \item {\textbf{Call Center Operations Training}
        \begin{itemize}[leftmargin=1.5em, itemsep=0.2em]
          \item {Completed a school internship aimed at skill development. The experience primarily involved training for call center operations with limited exposure to technical work.}
        \end{itemize}}
    \end{cvitems}
  }

  \vspace{0.4cm}

  %------------------------------------------------

\end{cventries}
